### 2017-09-16 reports/thesis/book.tex
In thesis, typo corrected in Chapter 2, added notation for inference chapter.
Added references to CT.

CT scanning was invented by G. Hounsfield \citep{hounsfield1980computed} in the 1980's and it was mainly used for medical imaging. The setup for CT scanning is different when scanning patients because the detector and X-ray source rotates around the patient \citep{cantatore2011introduction}. Recently CT has been used industrially for non-destructive testing in manufacturing \citep{cantatore2011introduction}. One possible application would be inspecting 3D printed samples \citep{villarraga2015assessing}. Other uses in science include the investigation of batteries \citep{o2017investigating} and materials \citep{wang2017x} \citep{zhang2016x}.

@@

The compound Poisson can be formally written. Let $Y$ be the number of photons detected in a pixel for some time exposure $\tau$,
\begin{equation*}
Y\sim\poisson(\lambda)
\end{equation*}
and
\begin{equation*}
\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=1,2,3,\dotdotdot
\end{equation*}
where $\lambda>0$ is the Poisson rate parameter. Let $U_i$ be the energy of the $i$th photon in a pixel for i.i.d.~$i=1,2,3,\dotdotdot$ with p.d.f.~$p_U(u)$. Let $X$ be the greyvalue of a pixel and is an energy integrating detector, then
\begin{equation}
X|Y = \sum_{i=1}^{Y}U_i+\kappa
\label{eq:compoundPoisson_X|Y}
\end{equation}
where $\kappa$ is some offset. For now let $\kappa=0$, then the marginal $X$ has the compound Poisson distribution. The p.d.f.~of $X$ can be obtained by marginalising the joint p.d.f.
\begin{equation*}
p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \quad\text{for }x\geqslant 0\ .
\end{equation*}
However it should be noted that $X=0$ if and only if $Y=0$ with probability
\begin{equation*}
\prob(X=0)=\euler^{-\lambda} \ .
\end{equation*}
Formally $X$ has probability mass at $X=0$ and probability density at $X>0$, then 
\begin{equation}
p_X(x) = 
\begin{cases}
\delta(x) \euler^{-\lambda}  & \text{ for } x=0 \\ 
\sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} \quad\text{for } & \text{ for } x>0
\end{cases}
\end{equation}
where $\delta(x)$ is the Dirac delta function. It is quite often the case this cannot be written in closed form.

@@

If the distribution of $U$ cannot be obtained or estimated, then one can guess that distribution. \cite{xu2009electronic} for example used a Gamma distribution
\begin{equation}
U\sim\gammaDist\left(\alpha,\beta\right)
\end{equation}
where $\alpha>0$ is the Gamma shape parameter and $\beta>0$ is the Gamma rate parameter. This is a special case of the compound Poisson called the compound Poisson-Gamma model and one can write
\begin{equation}
X\sim\CPoisson(\lambda,\alpha,\beta) \ .
\end{equation}
The conditional distribution can be shown to be
\begin{equation}
X|Y\sim\gammaDist\left(Y\alpha,\lambda\right) \ .
\end{equation}

Using results derived earlier, the m.g.f.~of the of $X$ is
\begin{equation}
M(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
\end{equation}
and moments can be obtained from it such as
\begin{equation}
\expectation\left[X\right]=\frac{\alpha\lambda}{\beta}
\end{equation}
\begin{equation}
\variance\left[X\right]=\frac{\alpha(\alpha+1)\lambda}{\beta^2}
\label{eq:compoundPoisson_variance}
\end{equation}
and
\begin{equation}
\expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3} \ .
\end{equation}

The p.d.f.~can be shown to be
\begin{equation}
p_X(x) = 
\begin{cases}
\delta(x) \euler^{-\lambda} & \text{ for } x=x \\ 
\sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
\end{cases}
\label{eq:compoundPoisson_pdf}
\end{equation}
and it is well known the infinite sum cannot be written in closed form. There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}. Of course direction simulation of a compound Poisson-Gamma random variable is incredibly easy if $U$ can be simulated. The p.d.f.~then can be estimated using these simulated samples.

@@

>>>>

CT was solved theoretically by \cite{cormack1973reconstruction} and implemented  by \cite{hounsfield1973computerized} \citep{hounsfield1980computed}. It was mainly used for medical imaging. The setup for CT scanning is different when scanning patients because the detector and X-ray source rotates around the patient \citep{cantatore2011introduction}. Recently CT has been used industrially for non-destructive testing in manufacturing \citep{cantatore2011introduction}. One possible application would be inspecting 3D printed samples \citep{villarraga2015assessing}. Other uses in science include the investigation of batteries \citep{o2017investigating} and materials \citep{wang2017x} \citep{zhang2016x}.

@@

The compound Poisson can be formally written. Let $Y$ be the number of photons detected in a pixel for some time exposure $\tau$,
\begin{equation*}
Y\sim\poisson(\lambda)
\end{equation*}
that is
\begin{equation*}
\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=0,1,2,\dotdotdot
\end{equation*}
where $\lambda>0$ is the Poisson rate parameter. Let $U_i$ be the energy of the $i$th photon in a pixel for i.i.d.~$i=1,2,3,\dotdotdot$ with p.d.f.~$p_U(u)$. Let $X$ be the greyvalue of a pixel and is an energy integrating detector, then
\begin{equation}
X|Y = \sum_{i=1}^{Y}U_i+\kappa
\label{eq:compoundPoisson_X|Y}
\end{equation}
where $\kappa$ is some offset. For now let $\kappa=0$, then the marginal $X$ has the compound Poisson distribution. The p.d.f.~of $X$ can be obtained by marginalising the joint p.d.f.
\begin{equation*}
p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \quad\text{for }x\geqslant 0\ .
\end{equation*}
However it should be noted that $X=0$ if and only if $Y=0$ with probability
\begin{equation*}
\prob(X=0)=\euler^{-\lambda} \ .
\end{equation*}
Formally $X$ has probability mass at $X=0$ and probability density at $X>0$, then 
\begin{equation}
p_X(x) = 
\begin{cases}
\delta(x) \euler^{-\lambda}  & \text{ for } x=0 \\ 
\sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} \quad\text{for } & \text{ for } x>0
\end{cases}
\end{equation}
where $\delta(x)$ is the Dirac delta function. It is quite often the case this cannot be written in closed form.

@@

If the distribution of $U$ cannot be obtained or estimated, then one can guess that distribution. \cite{xu2009electronic} for example used a Gamma distribution
\begin{equation}
U\sim\gammaDist\left(\alpha,\beta\right)
\end{equation}
where $\alpha>0$ is the Gamma shape parameter and $\beta>0$ is the Gamma rate parameter. This is a special case of the compound Poisson called the compound Poisson-Gamma model and one can write
\begin{equation}
X\sim\CPoisson(\lambda,\alpha,\beta) \ .
\end{equation}
The conditional distribution can be shown to be
\begin{equation}
X|Y\sim\gammaDist\left(Y\alpha,\beta\right) \ .
\end{equation}

Using results derived earlier, the m.g.f.~of the of $X$ is
\begin{equation}
M_X(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
\end{equation}
and moments can be obtained from it such as
\begin{equation}
\expectation\left[X\right]=\frac{\alpha\lambda}{\beta}
\end{equation}
\begin{equation}
\variance\left[X\right]=\frac{\alpha(\alpha+1)\lambda}{\beta^2}
\label{eq:compoundPoisson_variance}
\end{equation}
and
\begin{equation}
\expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3} \ .
\end{equation}

The p.d.f.~can be shown to be
\begin{equation}
p_X(x) = 
\begin{cases}
\delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
\sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
\end{cases}
\label{eq:compoundPoisson_pdf}
\end{equation}
and it is well known the infinite sum cannot be written in closed form. There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}. Of course direct simulation of a compound Poisson-Gamma random variable is incredibly easy if $U$ can be simulated. The p.d.f.~then can be estimated using these simulated samples.

@@

%\begin{equation*}
%i=1,2,3,\dotdotdot,n_{pixel}
%\end{equation*}
%\begin{equation*}
%j=1,2,3,\dotdotdot,n_{repeat}
%\end{equation*}
%\begin{equation*}
%x_i^{(j)} = \text{mean greyvalue of pixel }i\text{, }j\text{th repeat}
%\end{equation*}
%\begin{equation*}
%y_i^{(j)} = \text{variance greyvalue of pixel }i\text{, }j\text{th repeat}
%\end{equation*}
%\begin{equation*}
%\widehat{Y}^{(j)}(x) = \text{predicted variance greyvalue given }x
%\end{equation*}
%Trained $\widehat{Y}^{(j)}(x)$ using $(y_1^{(j)},x_1^{(j)}),(y_2^{(j)},x_2^{(j)}),(y_3^{(j)},x_3^{(j)}),\dotdotdot,(y_{n_{pixel}}^{(j)},x_{n_{pixel}}^{(j)})$.
%\begin{equation*}
%\widehat{\zeta}^{(j)}(x) = \text{predicted variance of the variance greyvalue given }x
%\end{equation*}
%
%Below are the training statistics, but can be generalised to test statistics:
%\begin{equation}
%\text{MSE}^{(j)} = \sum_{i=1}^{n_{pixel}} \left[\widehat{Y}^{(j)}(x_i^{(j)}) - y_i^{(j)}\right]^2
%\end{equation}
%\begin{equation}
%\text{MSSE}^{(j)} = \sum_{i=1}^{n_{pixel}} \left[\dfrac{\widehat{Y}^{(j)}(x_i^{(j)}) - y_i^{(j)}}{\sqrt{\widehat{\zeta}^{(j)}(x_i^{(j)})}}\right]^2
%\end{equation}
%\begin{equation}
%\text{VAR}^{(j)} = \sum_{i=1}^{n_{pixel}}
%\left[
%\widehat{Y}^{(j)}(x_i^{(j)}) - \expectation(\widehat{Y}(x_i^{(j)}))
%\right]^2
%\end{equation}
%\begin{equation}
%\text{BIAS2}^{(j)} = \sum_{i=1}^{n_{pixel}}
%\left[
%\expectation(\widehat{Y}(x_i^{(j)}))
%-
%y_i^{(j)}
%\right]^2
%\end{equation}
%where
%\begin{equation}
%\expectation(\widehat{Y}(x_i^{(j)})) \approx
%\frac{1}{n_{repeat}}\sum_{j=1}^{n_{repeat}}
%\widehat{Y}^{(j)}(x_i^{(j)})
%\end{equation}
%
%\clearpage
%\begin{equation}
%Y(x) = y(x) + \epsilon(x)
%\end{equation}
%where
%\begin{equation}
%\expectation[\epsilon(x)] = 0, \quad \variance[\epsilon(x)] = \sigma^2(x) \ .
%\end{equation}
%The statistics for a given $x$ are:
%\begin{equation}
%\text{MSE}(x) = \expectation\left[
%(Y(x)-\widehat{Y}(x))^2
%\right]
%\end{equation}
%\begin{equation}
%\text{VAR}(x) = \expectation\left[
%(\widehat{Y}(x) - \expectation(\widehat{Y}(x))^2
%\right]
%\end{equation}
%\begin{equation}
%\text{BIAS2}(x) = \expectation\left[
%(\expectation(\widehat{Y}(x) - y(x))^2
%\right]
%\end{equation}
%\begin{equation}
%\sigma^2(x) = \expectation\left[
%(
%Y(x) - \expectation(Y(x))
%)^2
%\right] \ .
%\end{equation}
%
%$y(x)$ is unknown so the bias squared can be calculated using
%\begin{equation}
%\text{BIAS2}(X) = \text{MSE}(X) - \text{VAR}(X) - \sigma^2(x)
%\end{equation}
%
%The expectations were estimated using bootstrapped samples of $Y(x)$ and $\widehat{Y}(x)$.
%
%\clearpage
%
%\begin{figure}
%\centering
%    \centerline{
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/training_MSSE.eps}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/test_MSSE.eps}
%    \end{subfigure}
%    }
%    \caption{Mean squared standardised error}
%\end{figure}
%
%\begin{figure}
%\centering
%    \centerline{
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/training_MSE.eps}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/test_MSE.eps}
%    \end{subfigure}
%    }
%    \caption{Mean squared error}
%\end{figure}
%
%\begin{figure}
%\centering
%    \centerline{
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/training_var.eps}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/test_var.eps}
%    \end{subfigure}
%    }
%    \caption{Estimation variance}
%\end{figure}
%
%\begin{figure}
%\centering
%    \centerline{
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/training_bias2.eps}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/test_bias2.eps}
%    \end{subfigure}
%    }
%    \caption{Bias squared}
%\end{figure}
